DDD plots

### 2017-01-01 analysis/metaplot_examples.Rmd
Revised chunk labels for metaplot_examples.Rmd.

```{r shrunk}
metaplot(get_pm(beta.ash)[i],get_psd(beta.ash)[i],
         ylab = "",xlab = "",xlim = c(-6,6),
         colors = meta.colors(box = c(rep("red",n/2),rep("black",n/2))[i]))
```

>>>>

```{r plot_shrunk}
metaplot(get_pm(beta.ash)[i],get_psd(beta.ash)[i],
         ylab = "",xlab = "",xlim = c(-6,6),
         colors = meta.colors(box = c(rep("red",n/2),rep("black",n/2))[i]))
```
